```{r}
library(dplyr)
library(elo)
library(tidyverse)
```

Wyoming invite. This chunk has been edited, it was originally written to join with results from the previous year but I changed my mind about doing that.

## double hashtags are comments that were the code for the previous version
```{r}
## full <- read.csv("2017 national_regional/2017 national regional mens individual/elo updated/2017 men elo.csv")
## full <- subset (full, select = -X)
df <- read.csv("2018 invitationals/2018 invitationals mens individual/2018 wyoming invite mens individual 8_31.csv")

# run the joins
## df <- list(wy, full)
# merge all data frames in list
## df <- df %>% reduce(left_join, by= c('NAME', 'TEAM'))

#set new runners elos to 1000
## df[is.na(df)] = 0
## df$elo <- ifelse(df$elo == 0, 1000, df$elo)
df$elo <- 1000

#create a column for temporary storage of the elo update
df$update <- 0


for (i in df$PL){ # loop through the data frame
  
  y = i # create a second number to isolate into pairs of racers
  
  repeat{
    if(y >= nrow(df)) {break} # exit if the second runner number gets beyond the dataframe
    #if((y - i) > 100) {break} # exit if the second number is more than 150 places from the first number
    # beating runners by a ton doesn't matter
    
    y = y + 1 # sets the y to be the next runner
    
    # edit the update column, its the elo update from the pair, multiplied by whats essentially the percentile
    # 1 - place in the race, divided by nrow, rounded. So finishing first is 0.99, finishing last is just 0
    
    df[i,'update'] <- df[i,'update'] + (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[y, 'PL']/nrow(df), digits = 2)))
    
    df[y,'update'] <- df[y,'update'] - (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[i, 'PL']/nrow(df), digits = 2)))
    
  }
}

#this just means the update is slightly less drastic
## df$elo <- df$elo + (df$update / nrow(df)) * 100

# a new elo update, switching to adding the raw score
df$elo <- df$elo + df$update

#df$elo <- df$elo + (df$update * (1 - round(df$PL/nrow(df), digits = 2)))/4

# cut the df down to just name, team, elo
df2 <- df %>% select(NAME, TEAM, elo)

#now join the update back onto the main one
## new_full <- list(full, df2)
#merge all data frames in list
## new_full <- new_full %>% reduce(full_join, by= c('NAME', 'TEAM'))

# now replace the old elo's with the greater ones
## new_full[is.na(new_full)] = 0
## new_full$elo <- ifelse(new_full$elo.y > new_full$elo.x, new_full$elo.y, new_full$elo.x)

#then cut it back down to just name, team, elo
## new_full <- new_full %>% select(NAME, TEAM, elo)

write.csv(df2,"2018 elo.csv")
```

Oregon preview
```{r}
#Load in data
full <- read.csv("2018 elo.csv")
full <- subset (full, select = -X)
x <- read.csv("2018 invitationals/2018 invitationals mens individual/2018 oregon preview mens individual 09_06.csv")

#run the joins
df <- list(x, full)
#merge all data frames in list
df <- df %>% reduce(left_join, by= c('NAME', 'TEAM'))

#set new runners elos to 1000
df[is.na(df)] = 0
df$elo <- ifelse(df$elo == 0, 1000, df$elo)

#create a column for temporary storage of the elo update
df$update <- 0


for (i in df$PL){ # loop through the data frame
  
  y = i # create a second number to isolate into pairs of racers
  
  repeat{
    if(y >= nrow(df)) {break} # exit if the second runner number gets beyond the dataframe
    #if((y - i) > 100) {break} # exit if the second number is more than 150 places from the first number
    # beating runners by a ton doesn't matter
    
    y = y + 1 # sets the y to be the next runner
    
    # edit the update column, its the elo update from the pair, multiplied by whats essentially the percentile
    # 1 - place in the race, divided by nrow, rounded. So finishing first is 0.99, finishing last is just 0
    
    df[i,'update'] <- df[i,'update'] + (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[y, 'PL']/nrow(df), digits = 2)))
    
    df[y,'update'] <- df[y,'update'] - (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[i, 'PL']/nrow(df), digits = 2)))
    
  }
}

#this just means the update is slightly less drastic

df$elo <- df$elo + df$update


# cut the df down to just name, team, elo
df2 <- df %>% select(NAME, TEAM, elo)

#now join the update back onto the main one
new_full <- list(full, df2)
#merge all data frames in list
new_full <- new_full %>% reduce(full_join, by= c('NAME', 'TEAM'))

# now replace the old elo's with the greater ones
new_full[is.na(new_full)] = 0
new_full$elo <- ifelse(new_full$elo.y > new_full$elo.x, new_full$elo.y, new_full$elo.x)

#then cut it back down to just name, team, elo
new_full <- new_full %>% select(NAME, TEAM, elo)

write.csv(new_full,"2018 elo.csv")
```

Auburn invite
```{r}
#Load in data
full <- read.csv("2018 elo.csv")
x <- read.csv("2018 invitationals/2018 invitationals mens individual/2018 auburn invite mens individual 09_07.csv")

#run the joins
df <- list(x, full)
#merge all data frames in list
df <- df %>% reduce(left_join, by= c('NAME', 'TEAM'))

#set new runners elos to 1000
df[is.na(df)] = 0
df$elo <- ifelse(df$elo == 0, 1000, df$elo)

#create a column for temporary storage of the elo update
df$update <- 0


for (i in df$PL){ # loop through the data frame
  
  y = i # create a second number to isolate into pairs of racers
  
  repeat{
    if(y >= nrow(df)) {break} # exit if the second runner number gets beyond the dataframe
    #if((y - i) > 100) {break} # exit if the second number is more than 150 places from the first number
    # beating runners by a ton doesn't matter
    
    y = y + 1 # sets the y to be the next runner
    
    # edit the update column, its the elo update from the pair, multiplied by whats essentially the percentile
    # 1 - place in the race, divided by nrow, rounded. So finishing first is 0.99, finishing last is just 0
    
    df[i,'update'] <- df[i,'update'] + (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[y, 'PL']/nrow(df), digits = 2)))
    
    df[y,'update'] <- df[y,'update'] - (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[i, 'PL']/nrow(df), digits = 2)))
    
  }
}

#this just means the update is slightly less drastic

df$elo <- df$elo + df$update


# cut the df down to just name, team, elo
df2 <- df %>% select(NAME, TEAM, elo)

#now join the update back onto the main one
new_full <- list(full, df2)
#merge all data frames in list
new_full <- new_full %>% reduce(full_join, by= c('NAME', 'TEAM'))

# now replace the old elo's with the greater ones
new_full[is.na(new_full)] = 0
new_full$elo <- ifelse(new_full$elo.y > new_full$elo.x, new_full$elo.y, new_full$elo.x)

#then cut it back down to just name, team, elo
new_full <- new_full %>% select(NAME, TEAM, elo)

write.csv(new_full,"2018 elo.csv")
```

Bill Dellinger
```{r}
#Load in data
full <- read.csv("2018 elo.csv")
x <- read.csv("2018 invitationals/2018 invitationals mens individual/2018 bill dellinger mens individual 09_21.csv")

#run the joins
df <- list(x, full)
#merge all data frames in list
df <- df %>% reduce(left_join, by= c('NAME', 'TEAM'))

#set new runners elos to 1000
df[is.na(df)] = 0
df$elo <- ifelse(df$elo == 0, 1000, df$elo)

#create a column for temporary storage of the elo update
df$update <- 0


for (i in df$PL){ # loop through the data frame
  
  y = i # create a second number to isolate into pairs of racers
  
  repeat{
    if(y >= nrow(df)) {break} # exit if the second runner number gets beyond the dataframe
    #if((y - i) > 100) {break} # exit if the second number is more than 150 places from the first number
    # beating runners by a ton doesn't matter
    
    y = y + 1 # sets the y to be the next runner
    
    # edit the update column, its the elo update from the pair, multiplied by whats essentially the percentile
    # 1 - place in the race, divided by nrow, rounded. So finishing first is 0.99, finishing last is just 0
    
    df[i,'update'] <- df[i,'update'] + (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[y, 'PL']/nrow(df), digits = 2)))
    
    df[y,'update'] <- df[y,'update'] - (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[i, 'PL']/nrow(df), digits = 2)))
    
  }
}

#this just means the update is slightly less drastic

df$elo <- df$elo + df$update


# cut the df down to just name, team, elo
df2 <- df %>% select(NAME, TEAM, elo)

#now join the update back onto the main one
new_full <- list(full, df2)
#merge all data frames in list
new_full <- new_full %>% reduce(full_join, by= c('NAME', 'TEAM'))

# now replace the old elo's with the greater ones
new_full[is.na(new_full)] = 0
new_full$elo <- ifelse(new_full$elo.y > new_full$elo.x, new_full$elo.y, new_full$elo.x)

#then cut it back down to just name, team, elo
new_full <- new_full %>% select(NAME, TEAM, elo)

write.csv(new_full,"2018 elo.csv")
```

Battle in Beantown
```{r}
#Load in data
full <- read.csv("2018 elo.csv")
full <- subset (full, select = -X)
x <- read.csv("2018 invitationals/2018 invitationals mens individual/2018 coast to coast battle in beantown mens individual 09_21.csv")

#run the joins
df <- list(x, full)
#merge all data frames in list
df <- df %>% reduce(left_join, by= c('NAME', 'TEAM'))

#set new runners elos to 1000
df[is.na(df)] = 0
df$elo <- ifelse(df$elo == 0, 1000, df$elo)

#create a column for temporary storage of the elo update
df$update <- 0


for (i in df$PL){ # loop through the data frame
  
  y = i # create a second number to isolate into pairs of racers
  
  repeat{
    if(y >= nrow(df)) {break} # exit if the second runner number gets beyond the dataframe
    #if((y - i) > 100) {break} # exit if the second number is more than 150 places from the first number
    # beating runners by a ton doesn't matter
    
    y = y + 1 # sets the y to be the next runner
    
    # edit the update column, its the elo update from the pair, multiplied by whats essentially the percentile
    # 1 - place in the race, divided by nrow, rounded. So finishing first is 0.99, finishing last is just 0
    
    df[i,'update'] <- df[i,'update'] + (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[y, 'PL']/nrow(df), digits = 2)))
    
    df[y,'update'] <- df[y,'update'] - (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[i, 'PL']/nrow(df), digits = 2)))
    
  }
}

#this just means the update is slightly less drastic

df$elo <- df$elo + df$update


# cut the df down to just name, team, elo
df2 <- df %>% select(NAME, TEAM, elo)

#now join the update back onto the main one
new_full <- list(full, df2)
#merge all data frames in list
new_full <- new_full %>% reduce(full_join, by= c('NAME', 'TEAM'))

# now replace the old elo's with the greater ones
new_full[is.na(new_full)] = 0
new_full$elo <- ifelse(new_full$elo.y > new_full$elo.x, new_full$elo.y, new_full$elo.x)

#then cut it back down to just name, team, elo
new_full <- new_full %>% select(NAME, TEAM, elo)

write.csv(new_full,"2018 elo.csv")
```

Joe Piane Blue
```{r}
#Load in data
full <- read.csv("2018 elo.csv")
full <- subset (full, select = -X)
x <- read.csv("2018 invitationals/2018 invitationals mens individual/2018 joe piane blue mens individual 09_28.csv")

#run the joins
df <- list(x, full)
#merge all data frames in list
df <- df %>% reduce(left_join, by= c('NAME', 'TEAM'))

#set new runners elos to 1000
df[is.na(df)] = 0
df$elo <- ifelse(df$elo == 0, 1000, df$elo)

#create a column for temporary storage of the elo update
df$update <- 0


for (i in df$PL){ # loop through the data frame
  
  y = i # create a second number to isolate into pairs of racers
  
  repeat{
    if(y >= nrow(df)) {break} # exit if the second runner number gets beyond the dataframe
    #if((y - i) > 100) {break} # exit if the second number is more than 150 places from the first number
    # beating runners by a ton doesn't matter
    
    y = y + 1 # sets the y to be the next runner
    
    # edit the update column, its the elo update from the pair, multiplied by whats essentially the percentile
    # 1 - place in the race, divided by nrow, rounded. So finishing first is 0.99, finishing last is just 0
    
    df[i,'update'] <- df[i,'update'] + (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[y, 'PL']/nrow(df), digits = 2)))
    
    df[y,'update'] <- df[y,'update'] - (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[i, 'PL']/nrow(df), digits = 2)))
    
  }
}

#this just means the update is slightly less drastic

df$elo <- df$elo + df$update


# cut the df down to just name, team, elo
df2 <- df %>% select(NAME, TEAM, elo)

#now join the update back onto the main one
new_full <- list(full, df2)
#merge all data frames in list
new_full <- new_full %>% reduce(full_join, by= c('NAME', 'TEAM'))

# now replace the old elo's with the greater ones
new_full[is.na(new_full)] = 0
new_full$elo <- ifelse(new_full$elo.y > new_full$elo.x, new_full$elo.y, new_full$elo.x)

#then cut it back down to just name, team, elo
new_full <- new_full %>% select(NAME, TEAM, elo)

write.csv(new_full,"2018 elo.csv")
```

Joe Piane Gold
```{r}
#Load in data
full <- read.csv("2018 elo.csv")
full <- subset (full, select = -X)
x <- read.csv("2018 invitationals/2018 invitationals mens individual/2018 joe piane gold mens individual 09_28.csv")

#run the joins
df <- list(x, full)
#merge all data frames in list
df <- df %>% reduce(left_join, by= c('NAME', 'TEAM'))

#set new runners elos to 1000
df[is.na(df)] = 0
df$elo <- ifelse(df$elo == 0, 1000, df$elo)

#create a column for temporary storage of the elo update
df$update <- 0


for (i in df$PL){ # loop through the data frame
  
  y = i # create a second number to isolate into pairs of racers
  
  repeat{
    if(y >= nrow(df)) {break} # exit if the second runner number gets beyond the dataframe
    #if((y - i) > 100) {break} # exit if the second number is more than 150 places from the first number
    # beating runners by a ton doesn't matter
    
    y = y + 1 # sets the y to be the next runner
    
    # edit the update column, its the elo update from the pair, multiplied by whats essentially the percentile
    # 1 - place in the race, divided by nrow, rounded. So finishing first is 0.99, finishing last is just 0
    
    df[i,'update'] <- df[i,'update'] + (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[y, 'PL']/nrow(df), digits = 2)))
    
    df[y,'update'] <- df[y,'update'] - (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[i, 'PL']/nrow(df), digits = 2)))
    
  }
}

#this just means the update is slightly less drastic

df$elo <- df$elo + df$update


# cut the df down to just name, team, elo
df2 <- df %>% select(NAME, TEAM, elo)

#now join the update back onto the main one
new_full <- list(full, df2)
#merge all data frames in list
new_full <- new_full %>% reduce(full_join, by= c('NAME', 'TEAM'))

# now replace the old elo's with the greater ones
new_full[is.na(new_full)] = 0
new_full$elo <- ifelse(new_full$elo.y > new_full$elo.x, new_full$elo.y, new_full$elo.x)

#then cut it back down to just name, team, elo
new_full <- new_full %>% select(NAME, TEAM, elo)

write.csv(new_full,"2018 elo.csv")
```

Joe Piane Open
```{r}
#Load in data
full <- read.csv("2018 elo.csv")
full <- subset (full, select = -X)
x <- read.csv("2018 invitationals/2018 invitationals mens individual/2018 joe piane open mens individual 09_28.csv")

#run the joins
df <- list(x, full)
#merge all data frames in list
df <- df %>% reduce(left_join, by= c('NAME', 'TEAM'))

#set new runners elos to 1000
df[is.na(df)] = 0
df$elo <- ifelse(df$elo == 0, 1000, df$elo)

#create a column for temporary storage of the elo update
df$update <- 0


for (i in df$PL){ # loop through the data frame
  
  y = i # create a second number to isolate into pairs of racers
  
  repeat{
    if(y >= nrow(df)) {break} # exit if the second runner number gets beyond the dataframe
    #if((y - i) > 100) {break} # exit if the second number is more than 150 places from the first number
    # beating runners by a ton doesn't matter
    
    y = y + 1 # sets the y to be the next runner
    
    # edit the update column, its the elo update from the pair, multiplied by whats essentially the percentile
    # 1 - place in the race, divided by nrow, rounded. So finishing first is 0.99, finishing last is just 0
    
    df[i,'update'] <- df[i,'update'] + (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[y, 'PL']/nrow(df), digits = 2)))
    
    df[y,'update'] <- df[y,'update'] - (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[i, 'PL']/nrow(df), digits = 2)))
    
  }
}

#this just means the update is slightly less drastic

df$elo <- df$elo + df$update


# cut the df down to just name, team, elo
df2 <- df %>% select(NAME, TEAM, elo)

#now join the update back onto the main one
new_full <- list(full, df2)
#merge all data frames in list
new_full <- new_full %>% reduce(full_join, by= c('NAME', 'TEAM'))

# now replace the old elo's with the greater ones
new_full[is.na(new_full)] = 0
new_full$elo <- ifelse(new_full$elo.y > new_full$elo.x, new_full$elo.y, new_full$elo.x)

#then cut it back down to just name, team, elo
new_full <- new_full %>% select(NAME, TEAM, elo)

write.csv(new_full,"2018 elo.csv")
```

Nuttycombe B
```{r}
#Load in data
full <- read.csv("2018 elo.csv")
full <- subset (full, select = -X)
x <- read.csv("2018 invitationals/2018 invitationals mens individual/2018 nuttycombe b race mens individual 09_28.csv")

#run the joins
df <- list(x, full)
#merge all data frames in list
df <- df %>% reduce(left_join, by= c('NAME', 'TEAM'))

#set new runners elos to 1000
df[is.na(df)] = 0
df$elo <- ifelse(df$elo == 0, 1000, df$elo)

#create a column for temporary storage of the elo update
df$update <- 0


for (i in df$PL){ # loop through the data frame
  
  y = i # create a second number to isolate into pairs of racers
  
  repeat{
    if(y >= nrow(df)) {break} # exit if the second runner number gets beyond the dataframe
    #if((y - i) > 100) {break} # exit if the second number is more than 150 places from the first number
    # beating runners by a ton doesn't matter
    
    y = y + 1 # sets the y to be the next runner
    
    # edit the update column, its the elo update from the pair, multiplied by whats essentially the percentile
    # 1 - place in the race, divided by nrow, rounded. So finishing first is 0.99, finishing last is just 0
    
    df[i,'update'] <- df[i,'update'] + (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[y, 'PL']/nrow(df), digits = 2)))
    
    df[y,'update'] <- df[y,'update'] - (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[i, 'PL']/nrow(df), digits = 2)))
    
  }
}

#this just means the update is slightly less drastic

df$elo <- df$elo + df$update


# cut the df down to just name, team, elo
df2 <- df %>% select(NAME, TEAM, elo)

#now join the update back onto the main one
new_full <- list(full, df2)
#merge all data frames in list
new_full <- new_full %>% reduce(full_join, by= c('NAME', 'TEAM'))

# now replace the old elo's with the greater ones
new_full[is.na(new_full)] = 0
new_full$elo <- ifelse(new_full$elo.y > new_full$elo.x, new_full$elo.y, new_full$elo.x)

#then cut it back down to just name, team, elo
new_full <- new_full %>% select(NAME, TEAM, elo)

write.csv(new_full,"2018 elo.csv")
```

Nuttycombe
```{r}
#Load in data
full <- read.csv("2018 elo.csv")
full <- subset (full, select = -X)
x <- read.csv("2018 invitationals/2018 invitationals mens individual/2018 nuttycombe mens individual 09_28.csv")

#run the joins
df <- list(x, full)
#merge all data frames in list
df <- df %>% reduce(left_join, by= c('NAME', 'TEAM'))

#set new runners elos to 1000
df[is.na(df)] = 0
df$elo <- ifelse(df$elo == 0, 1000, df$elo)

#create a column for temporary storage of the elo update
df$update <- 0


for (i in df$PL){ # loop through the data frame
  
  y = i # create a second number to isolate into pairs of racers
  
  repeat{
    if(y >= nrow(df)) {break} # exit if the second runner number gets beyond the dataframe
    #if((y - i) > 100) {break} # exit if the second number is more than 150 places from the first number
    # beating runners by a ton doesn't matter
    
    y = y + 1 # sets the y to be the next runner
    
    # edit the update column, its the elo update from the pair, multiplied by whats essentially the percentile
    # 1 - place in the race, divided by nrow, rounded. So finishing first is 0.99, finishing last is just 0
    
    df[i,'update'] <- df[i,'update'] + (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[y, 'PL']/nrow(df), digits = 2)))
    
    df[y,'update'] <- df[y,'update'] - (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[i, 'PL']/nrow(df), digits = 2)))
    
  }
}

#this just means the update is slightly less drastic

df$elo <- df$elo + df$update


# cut the df down to just name, team, elo
df2 <- df %>% select(NAME, TEAM, elo)

#now join the update back onto the main one
new_full <- list(full, df2)
#merge all data frames in list
new_full <- new_full %>% reduce(full_join, by= c('NAME', 'TEAM'))

# now replace the old elo's with the greater ones
new_full[is.na(new_full)] = 0
new_full$elo <- ifelse(new_full$elo.y > new_full$elo.x, new_full$elo.y, new_full$elo.x)

#then cut it back down to just name, team, elo
new_full <- new_full %>% select(NAME, TEAM, elo)

write.csv(new_full,"2018 elo.csv")
```

Stanford
```{r}
#Load in data
full <- read.csv("2018 elo.csv")
full <- subset (full, select = -X)
x <- read.csv("2018 invitationals/2018 invitationals mens individual/2018 stanford invite mens individual 09_29.csv")

#run the joins
df <- list(x, full)
#merge all data frames in list
df <- df %>% reduce(left_join, by= c('NAME', 'TEAM'))

#set new runners elos to 1000
df[is.na(df)] = 0
df$elo <- ifelse(df$elo == 0, 1000, df$elo)

#create a column for temporary storage of the elo update
df$update <- 0


for (i in df$PL){ # loop through the data frame
  
  y = i # create a second number to isolate into pairs of racers
  
  repeat{
    if(y >= nrow(df)) {break} # exit if the second runner number gets beyond the dataframe
    
    y = y + 1 # sets the y to be the next runner
    
    # edit the update column, its the elo update from the pair, multiplied by whats essentially the percentile
    # 1 - place in the race, divided by nrow, rounded. So finishing first is 0.99, finishing last is just 0
    
    df[i,'update'] <- df[i,'update'] + (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[y, 'PL']/nrow(df), digits = 2)))
    
    df[y,'update'] <- df[y,'update'] - (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[i, 'PL']/nrow(df), digits = 2)))
    
  }
}

#this just means the update is slightly less drastic

df$elo <- df$elo + df$update


# cut the df down to just name, team, elo
df2 <- df %>% select(NAME, TEAM, elo)

#now join the update back onto the main one
new_full <- list(full, df2)
#merge all data frames in list
new_full <- new_full %>% reduce(full_join, by= c('NAME', 'TEAM'))

# now replace the old elo's with the greater ones
new_full[is.na(new_full)] = 0
new_full$elo <- ifelse(new_full$elo.y > new_full$elo.x, new_full$elo.y, new_full$elo.x)

#then cut it back down to just name, team, elo
new_full <- new_full %>% select(NAME, TEAM, elo)

write.csv(new_full,"2018 elo.csv")
```

Penn St open
```{r}
#Load in data
full <- read.csv("2018 elo.csv")
full <- subset (full, select = -X)
x <- read.csv("2018 invitationals/2018 invitationals mens individual/2018 penn st open nationals mens individual 10_12.csv")

#run the joins
df <- list(x, full)
#merge all data frames in list
df <- df %>% reduce(left_join, by= c('NAME', 'TEAM'))

#set new runners elos to 1000
df[is.na(df)] = 0
df$elo <- ifelse(df$elo == 0, 1000, df$elo)

#create a column for temporary storage of the elo update
df$update <- 0


for (i in df$PL){ # loop through the data frame
  
  y = i # create a second number to isolate into pairs of racers
  
  repeat{
    if(y >= nrow(df)) {break} # exit if the second runner number gets beyond the dataframe
    
    y = y + 1 # sets the y to be the next runner
    
    # edit the update column, its the elo update from the pair, multiplied by whats essentially the percentile
    # 1 - place in the race, divided by nrow, rounded. So finishing first is 0.99, finishing last is just 0
    
    df[i,'update'] <- df[i,'update'] + (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[y, 'PL']/nrow(df), digits = 2)))
    
    df[y,'update'] <- df[y,'update'] - (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[i, 'PL']/nrow(df), digits = 2)))
    
  }
}

#this just means the update is slightly less drastic

df$elo <- df$elo + df$update


# cut the df down to just name, team, elo
df2 <- df %>% select(NAME, TEAM, elo)

#now join the update back onto the main one
new_full <- list(full, df2)
#merge all data frames in list
new_full <- new_full %>% reduce(full_join, by= c('NAME', 'TEAM'))

# now replace the old elo's with the greater ones
new_full[is.na(new_full)] = 0
new_full$elo <- ifelse(new_full$elo.y > new_full$elo.x, new_full$elo.y, new_full$elo.x)

#then cut it back down to just name, team, elo
new_full <- new_full %>% select(NAME, TEAM, elo)

write.csv(new_full,"2018 elo.csv")
```

Princeton
```{r}
#Load in data
full <- read.csv("2018 elo.csv")
full <- subset (full, select = -X)
x <- read.csv("2018 invitationals/2018 invitationals mens individual/2018 princeton invite mens individual 10_12.csv")

#run the joins
df <- list(x, full)
#merge all data frames in list
df <- df %>% reduce(left_join, by= c('NAME', 'TEAM'))

#set new runners elos to 1000
df[is.na(df)] = 0
df$elo <- ifelse(df$elo == 0, 1000, df$elo)

#create a column for temporary storage of the elo update
df$update <- 0


for (i in df$PL){ # loop through the data frame
  
  y = i # create a second number to isolate into pairs of racers
  
  repeat{
    if(y >= nrow(df)) {break} # exit if the second runner number gets beyond the dataframe
    
    y = y + 1 # sets the y to be the next runner
    
    # edit the update column, its the elo update from the pair, multiplied by whats essentially the percentile
    # 1 - place in the race, divided by nrow, rounded. So finishing first is 0.99, finishing last is just 0
    
    df[i,'update'] <- df[i,'update'] + (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[y, 'PL']/nrow(df), digits = 2)))
    
    df[y,'update'] <- df[y,'update'] - (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[i, 'PL']/nrow(df), digits = 2)))
    
  }
}

#this just means the update is slightly less drastic

df$elo <- df$elo + df$update


# cut the df down to just name, team, elo
df2 <- df %>% select(NAME, TEAM, elo)

#now join the update back onto the main one
new_full <- list(full, df2)
#merge all data frames in list
new_full <- new_full %>% reduce(full_join, by= c('NAME', 'TEAM'))

# now replace the old elo's with the greater ones
new_full[is.na(new_full)] = 0
new_full$elo <- ifelse(new_full$elo.y > new_full$elo.x, new_full$elo.y, new_full$elo.x)

#then cut it back down to just name, team, elo
new_full <- new_full %>% select(NAME, TEAM, elo)

write.csv(new_full,"2018 elo.csv")
```

Wisco Pre Nat Cardinal
```{r}
#Load in data
full <- read.csv("2018 elo.csv")
full <- subset (full, select = -X)
x <- read.csv("2018 invitationals/2018 invitationals mens individual/2018 wisconsin pre nationals cardinal mens individual 10_13.csv")

#run the joins
df <- list(x, full)
#merge all data frames in list
df <- df %>% reduce(left_join, by= c('NAME', 'TEAM'))

#set new runners elos to 1000
df[is.na(df)] = 0
df$elo <- ifelse(df$elo == 0, 1000, df$elo)

#create a column for temporary storage of the elo update
df$update <- 0


for (i in df$PL){ # loop through the data frame
  
  y = i # create a second number to isolate into pairs of racers
  
  repeat{
    if(y >= nrow(df)) {break} # exit if the second runner number gets beyond the dataframe
    
    y = y + 1 # sets the y to be the next runner
    
    # edit the update column, its the elo update from the pair, multiplied by whats essentially the percentile
    # 1 - place in the race, divided by nrow, rounded. So finishing first is 0.99, finishing last is just 0
    
    df[i,'update'] <- df[i,'update'] + (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[y, 'PL']/nrow(df), digits = 2)))
    
    df[y,'update'] <- df[y,'update'] - (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[i, 'PL']/nrow(df), digits = 2)))
    
  }
}

#this just means the update is slightly less drastic

df$elo <- df$elo + df$update


# cut the df down to just name, team, elo
df2 <- df %>% select(NAME, TEAM, elo)

#now join the update back onto the main one
new_full <- list(full, df2)
#merge all data frames in list
new_full <- new_full %>% reduce(full_join, by= c('NAME', 'TEAM'))

# now replace the old elo's with the greater ones
new_full[is.na(new_full)] = 0
new_full$elo <- ifelse(new_full$elo.y > new_full$elo.x, new_full$elo.y, new_full$elo.x)

#then cut it back down to just name, team, elo
new_full <- new_full %>% select(NAME, TEAM, elo)

write.csv(new_full,"2018 elo.csv")
```

Wisco Pre Nat Gray
```{r}
#Load in data
full <- read.csv("2018 elo.csv")
full <- subset (full, select = -X)
x <- read.csv("2018 invitationals/2018 invitationals mens individual/2018 wisconsin pre nationals gray mens individual 10_13.csv")

#run the joins
df <- list(x, full)
#merge all data frames in list
df <- df %>% reduce(left_join, by= c('NAME', 'TEAM'))

#set new runners elos to 1000
df[is.na(df)] = 0
df$elo <- ifelse(df$elo == 0, 1000, df$elo)

#create a column for temporary storage of the elo update
df$update <- 0


for (i in df$PL){ # loop through the data frame
  
  y = i # create a second number to isolate into pairs of racers
  
  repeat{
    if(y >= nrow(df)) {break} # exit if the second runner number gets beyond the dataframe
    
    y = y + 1 # sets the y to be the next runner
    
    # edit the update column, its the elo update from the pair, multiplied by whats essentially the percentile
    # 1 - place in the race, divided by nrow, rounded. So finishing first is 0.99, finishing last is just 0
    
    df[i,'update'] <- df[i,'update'] + (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[y, 'PL']/nrow(df), digits = 2)))
    
    df[y,'update'] <- df[y,'update'] - (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[i, 'PL']/nrow(df), digits = 2)))
    
  }
}

#this just means the update is slightly less drastic

df$elo <- df$elo + df$update


# cut the df down to just name, team, elo
df2 <- df %>% select(NAME, TEAM, elo)

#now join the update back onto the main one
new_full <- list(full, df2)
#merge all data frames in list
new_full <- new_full %>% reduce(full_join, by= c('NAME', 'TEAM'))

# now replace the old elo's with the greater ones
new_full[is.na(new_full)] = 0
new_full$elo <- ifelse(new_full$elo.y > new_full$elo.x, new_full$elo.y, new_full$elo.x)

#then cut it back down to just name, team, elo
new_full <- new_full %>% select(NAME, TEAM, elo)

write.csv(new_full,"2018 elo.csv")
```

Wisco Pre Nat White
```{r}
#Load in data
full <- read.csv("2018 elo.csv")
full <- subset (full, select = -X)
x <- read.csv("2018 invitationals/2018 invitationals mens individual/2018 wisconsin pre nationals white mens individual 10_13.csv")

#run the joins
df <- list(x, full)
#merge all data frames in list
df <- df %>% reduce(left_join, by= c('NAME', 'TEAM'))

#set new runners elos to 1000
df[is.na(df)] = 0
df$elo <- ifelse(df$elo == 0, 1000, df$elo)

#create a column for temporary storage of the elo update
df$update <- 0


for (i in df$PL){ # loop through the data frame
  
  y = i # create a second number to isolate into pairs of racers
  
  repeat{
    if(y >= nrow(df)) {break} # exit if the second runner number gets beyond the dataframe
    
    y = y + 1 # sets the y to be the next runner
    
    # edit the update column, its the elo update from the pair, multiplied by whats essentially the percentile
    # 1 - place in the race, divided by nrow, rounded. So finishing first is 0.99, finishing last is just 0
    
    df[i,'update'] <- df[i,'update'] + (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[y, 'PL']/nrow(df), digits = 2)))
    
    df[y,'update'] <- df[y,'update'] - (elo.update(c(1), c(df[i,'elo']), c(df[y,'elo']), k = 5) * 
                                          (1 - round(df[i, 'PL']/nrow(df), digits = 2)))
    
  }
}

#this just means the update is slightly less drastic

df$elo <- df$elo + df$update


# cut the df down to just name, team, elo
df2 <- df %>% select(NAME, TEAM, elo)

#now join the update back onto the main one
new_full <- list(full, df2)
#merge all data frames in list
new_full <- new_full %>% reduce(full_join, by= c('NAME', 'TEAM'))

# now replace the old elo's with the greater ones
new_full[is.na(new_full)] = 0
new_full$elo <- ifelse(new_full$elo.y > new_full$elo.x, new_full$elo.y, new_full$elo.x)

#then cut it back down to just name, team, elo
new_full <- new_full %>% select(NAME, TEAM, elo)

write.csv(new_full,"2018 elo.csv")
```

